Synthesis of Rules for Network Intrusion Detectors

### 2019-10-24 paper/paper.tex
acks

Active reconnaissance is a method used by malicious individuals to
gather information about vulnerabilities from a computing system. The
most common approach is to ``scan'' open ports to discover
vulnerabilities. Active reconnaissance is a preliminary step towards
an attack that actually exploits the system. A Ping Scan is a very
common type of port scan based on the ICMP
protocol. \Fix{...explain this attack...}

@@

\Fix{...}
%
% ---- Bibliography ----
%
% BibTeX users should specify bibliography style 'splncs04'.
% References will then be sorted and formatted in the correct style.
%
\bibliographystyle{splncs04}
\bibliography{references}
%

>>>>

Active reconnaissance is a method used by malicious individuals to
gather information about vulnerabilities from a computing system. The
most common approach is to ``scan'' open ports to discover
vulnerabilities. Active reconnaissance is a preliminary step towards
an attack that actually exploits the system. A Ping Scan is a very
common type of port scan based on the ICMP
protocol. \Luc{The attacker sends a set of ICMP Echo requests to a network of machines and sees which one responds to the request. This allow the attacker to know which machines are active in the network, then it can choose one of them to attack.}

@@

\section*{Acknowledgments}
This work is partially supported by RNP grant number 002951.

%
% ---- Bibliography ----
%
% BibTeX users should specify bibliography style 'splncs04'.
% References will then be sorted and formatted in the correct style.
%
\bibliographystyle{splncs04}
\bibliography{references}
%
